The process of information spreading has many similarities with epidemiology, therefore the well known SIR-model was adapted\cite{complexsystems}.  The ``susceptibles'', are not aware of the information and are called ``ignorants'' within this work. ``Infected'' individuals know about the information and are willing to share it with other people, in other words they spread it and are therefore called ``spreaders''. The adaptation of the epidemiological term ``recovered'' is not that straightforward as its meaning in this context is not entirely clear. However, they can be interpreted as individuals being aware of the information but do not share it with others. They are called "stiflers".
\\
\\
In the SIR-model as well as in the agent-based model, the following set of ``reaction equations'' was used (I: Ignorant, S: Spreader, R: Stifler):


\begin{empheq}[left=\empheqlbrace]{align}
& I + S \xrightarrow{\lambda} 2 S \\
& S + R \xrightarrow{\alpha} 2 R \\
& S + S \xrightarrow{\alpha} S + R 
\end{empheq}
\newline
The main difference to the standard SIR-model is that spreaders do not become stiflers spontaneously. This change is only induced by meeting another spreader or stifler.

\subsection{Homogeneous SIR model}

In the mathematical treatment of the homogeneous model, the set of differential equations is expressed in terms of the densities $i(t)=I(t)/N$, $s(t)=S(t)/N$ and $r(t)=R(t)/N$, where N is the number of individuals in the network.

\begin{empheq}[left=\empheqlbrace]{align}
& \frac{\text{d}i(t)}{\text{d}t} = -\lambda \cdot s(t)i(t) \\
& \frac{\text{d}s(t)}{\text{d}t} = \lambda \cdot s(t)i(t) - \alpha \cdot s(t)[s(t)+r(t)] \\
& \frac{\text{d}r(t)}{\text{d}t} = \alpha \cdot s(t)[s(t)+r(t)]
\end{empheq}



\subsection{Agent-based model}

In the inhomogeneous, agent-based model the individuals are connected in a certain manner (facebook friends in this particular work). Only connected agents are able to meet. If a meeting occurs, transitions are induced at a certain probability depending on the relation between the agents (details are discussed later). Additional to the different connectivity of the agents, they also have a different activity, i.e. different probability to meet somebody. 
\\
\\
To convert the reaction equations into an agent-based model, time was discretized and in each time step a series of two steps is performed. First, the agents randomly meet another agent they know or nobody. Only two-agent meetings are possible. In the second step, the status of the agents change corresponding to the situation. There are six possible combinations of ignorants, spreaders and stiflers. Three of them correspond to the ``reactions'' 1-3, the other ones (I+I, I+R and R+R) have no other influence than ``occupying'' the agents. The probability $\lambda$ was chosen to be dependent on the number of common friends. For simplicity, $\alpha$ was a constant.